### 2017-03-01 doc/Thesis/data/kinetics.tex
Thesis: adding conclusion

\pagebreak
\section{C5G7-TD Benchmark}

The C5G7 benchmark is a MOX fueled, pressurized water reactor (PWR) minicore configuration. The C5G7 geometry depicted in Fig. \ref{fig:c5g7-2D} comprises a 2-by-2 array of UO$_2$ and MOX assemblies surrounded by moderator. In Fig. \ref{fig:c5g7-2D} vacuum and reflective boundary conditions are denoted by V and R, respectively. The fuel pins are not homogenized, each pin cell is comprised of a fuel pin, fission chamber, or guide tube surrounded by moderator as depicted in Fig. \ref{fig:c5g7-pincell}. The cladding and gap are homogenized into the fuel and are not explicitly modeled. Each assembly is made up of a regular 17-by-17 grid of pin cells.
Seven energy-group cross sections for the seven material regions are given in \cite{c5g7}. The energy group boundaries are provided in Table \ref{tab:c5g7-ebounds}; three of the seven energy groups are fast, four are thermal.

\begin{figure}[!htpb]
\begin{center}
\includegraphics[width=\linewidth]{\FiguresDir/C5G7-2D.png}
\end{center}
\caption{Geometry of the two-dimensional C5G7 benchmark problem. Boundary conditions are vacuum (V) or reflective (R).}
\label{fig:c5g7-2D}
\end{figure}

\begin{figure}[!htpb]
\begin{center}
\includegraphics[width=0.5\linewidth]{\FiguresDir/C5G7-pincell.png}
\end{center}
\caption{Geometry of a C5G7 pin-cell.}
\label{fig:c5g7-pincell}
\end{figure}

\begin{table}[!htpb]
\centering
\caption{Energy group boundaries for C5G7 MOX benchmark.}
\label{tab:c5g7-ebounds}
\begin{tabular}{c c}
\hline
Group & Upper Energy\\
\hline
 1&20 MeV  \\
 2&1 MeV  \\
 3&500 keV  \\
 4&3 eV  \\
 5&0.625 MeV  \\
 6&0.1 MeV  \\
71&0.02 MeV  \\
\hline
\end{tabular}
\end{table}

\pagebreak
\section{LMW Benchmark?}

>>>>

%\pagebreak
%\section{C5G7-TD Benchmark}
%
%The C5G7 benchmark is a MOX fueled, pressurized water reactor (PWR) minicore configuration. The C5G7 geometry depicted in Fig. \ref{fig:c5g7-2D} comprises a 2-by-2 array of UO$_2$ and MOX assemblies surrounded by moderator. In Fig. \ref{fig:c5g7-2D} vacuum and reflective boundary conditions are denoted by V and R, respectively. The fuel pins are not homogenized, each pin cell is comprised of a fuel pin, fission chamber, or guide tube surrounded by moderator as depicted in Fig. \ref{fig:c5g7-pincell}. The cladding and gap are homogenized into the fuel and are not explicitly modeled. Each assembly is made up of a regular 17-by-17 grid of pin cells.
%Seven energy-group cross sections for the seven material regions are given in \cite{c5g7}. The energy group boundaries are provided in Table \ref{tab:c5g7-ebounds}; three of the seven energy groups are fast, four are thermal.
%
%\begin{figure}[!htpb]
%\begin{center}
%\includegraphics[width=\linewidth]{\FiguresDir/C5G7-2D.png}
%\end{center}
%\caption{Geometry of the two-dimensional C5G7 benchmark problem. Boundary conditions are vacuum (V) or reflective (R).}
%\label{fig:c5g7-2D}
%\end{figure}
%
%\begin{figure}[!htpb]
%\begin{center}
%\includegraphics[width=0.5\linewidth]{\FiguresDir/C5G7-pincell.png}
%\end{center}
%\caption{Geometry of a C5G7 pin-cell.}
%\label{fig:c5g7-pincell}
%\end{figure}
%
%\begin{table}[!htpb]
%\centering
%\caption{Energy group boundaries for C5G7 MOX benchmark.}
%\label{tab:c5g7-ebounds}
%\begin{tabular}{c c}
%\hline
%Group & Upper Energy\\
%\hline
% 1&20 MeV  \\
% 2&1 MeV  \\
% 3&500 keV  \\
% 4&3 eV  \\
% 5&0.625 MeV  \\
% 6&0.1 MeV  \\
%71&0.02 MeV  \\
%\hline
%\end{tabular}
%\end{table}
%
%\pagebreak
%\section{LMW Benchmark?}
